---
title: "Spectral analysis with Bonferroni correction"
output:
  html_notebook: default
  html_document: default
date: "10/9/2017"
---

### script info
update date: Oct 04,2017  
* This script is used to extract significant frequencies (p<0.05, corrected and uncorrected)  
* Visualize FFT results for each condition  

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(cowplot)
```

## Find significant frequencies

```{r}
# set important parameters

rm(list = ls())

fs <- 25
nfft <- 96 # refer to 'do_spectral.m'
pvalue <- 0.05

filepattern <- c("LP_Smoothed_")
```

### check uncorrected p values (<.05)
```{r echo=FALSE}
# put all data into a big list
constant <- c("Con100R_pvalue_uncor.txt","Con100L_pvalue_uncor.txt",
            "Con50R_invalid_pvalue_uncor.txt","Con50R_valid_pvalue_uncor.txt",
            "Con50L_invalid_pvalue_uncor.txt","Con50L_valid_pvalue_uncor.txt")

files <- paste0(filepattern,constant)

allconds <- vector("list",length(files))

for (i in seq_along(files)){
  allconds[[i]]<-as.vector(t(read.table(files[i]))) #convert the data frame to vector
}
names(allconds)<-files

# deal with each list
results<-vector("list",length(files))
p_hz<-vector("list",length(files))
for (i in seq_along(allconds)){
  p.val<-data.frame(allconds[[i]])
  p.val$Hz<-c((0:(nfft/2-1))*fs/nfft) # change it to c((0:nfft/2)*fs/nfft) if the nyquist frequency is included
  colnames(p.val)<-c("p","Hz")
  rownames(p.val)<-NULL
  p_hz[[i]]<-p.val  
  results[[i]]<-p.val %>% filter(p<=pvalue)
  }
names(results)<-files
names(p_hz)<-files

#check the results (uncorrected)
results 
```

### check out Bonferroni results

```{r echo=FALSE}
# deal with each list
results_bonf<-vector("list",length(files))
p_hz_bonf<-vector("list",length(files))
for (i in seq_along(allconds)){
  p.val_bonf<-data.frame(p.adjust(allconds[[i]],method='bonferroni'))
  p.val_bonf$Hz<-c((0:(nfft/2-1))*fs/nfft) # change it to c((0:nfft/2)*fs/nfft) if the nyquist frequency is included
  colnames(p.val_bonf)<-c("p","Hz")
  rownames(p.val_bonf)<-NULL
  p_hz_bonf[[i]]<-p.val_bonf  
  results_bonf[[i]]<-p.val_bonf %>% filter(p<=pvalue)
  }
names(results_bonf)<-files
names(p_hz_bonf)<-files

#check the results (uncorrected)
results_bonf
```

#### plot mean FFT results for all conditions

```{r echo=FALSE}

# prepare data
constantfft<-c('Con50L_invalid_allsub_ampli_mean.txt','Con50L_valid_allsub_ampli_mean.txt','Con50R_invalid_allsub_ampli_mean.txt',
            'Con50R_valid_allsub_ampli_mean.txt','Con100L_allsub_ampli_mean.txt','Con100R_allsub_ampli_mean.txt')

fftfiles<-paste0(filepattern, constantfft)

all_con<- fftfiles %>% map(read.table) %>% reduce(rbind)
  
trans_all_con<-data.frame(t(all_con))

colnames(trans_all_con)<-c("L_inval_50","L_val_50","R_inval_50","R_val_50",
                           "L_100","R_100")

trans_all_con$Hz<-c((0:(nfft/2-1))*fs/nfft)
rownames(trans_all_con)<-NULL
long_all_con<- trans_all_con %>% gather(Conditions,Amplitude,L_inval_50:R_100)
long_all_con$Conditions<-factor(long_all_con$Conditions, levels=(c("L_100","R_100","L_val_50","L_inval_50","R_val_50","R_inval_50")))
```

* prepare data for each condition

```{r echo=FALSE}
left_50<-long_all_con %>% filter(Conditions=="L_val_50"| Conditions=="L_inval_50")
right_50<-long_all_con %>% filter(Conditions=="R_val_50"| Conditions=="R_inval_50")
con100<-long_all_con %>% filter(Conditions=="L_100"| Conditions=="R_100")

```

* plot average FFT results 

Congruent/Incongruent in 50% cue condition in **left visual field**:

```{r echo=FALSE}
plot_L50<-ggplot(left_50,aes(x=Hz,y=Amplitude,color=Conditions))+geom_line(size=1.5,alpha=0.7)+
  scale_color_manual(values=c("#E6352F7F","#3D79F37F"),labels=c("Congruent","Incongruent"))+
  xlab("Frequency (Hz)")+ylab("Spectral Amplitude")+
  guides(color=guide_legend(title=NULL))+theme_classic()+
  theme(axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=16),legend.position="none")+
  scale_x_continuous(breaks=seq(0,12,2))
  #+theme(legend.position="top")+ggtitle("FFT of 50% Valid Condition in LVF")
plot_L50
```

Congruent/Incongruent in 50% cue condition in **right visual field**:
```{r echo=FALSE}
plot_R50<-ggplot(right_50,aes(x=Hz,y=Amplitude,color=Conditions))+geom_line(size=1.5,alpha=0.7)+
  scale_color_manual(values=c("#E6352F7F","#3D79F37F"),labels=c("Congruent","Incongruent"))+
  xlab("Frequency (Hz)")+ylab("Spectral Amplitude")+
  guides(color=guide_legend(title=NULL))+theme_classic()+
  theme(axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=16),
        legend.position="none")+scale_x_continuous(breaks=seq(0,12,2))
plot_R50
```

100% cue condition in **left visual field**
```{r echo=FALSE}
con100_L<-con100 %>% filter(Conditions=='L_100')
plot_100L<-ggplot(con100_L,aes(x=Hz,y=Amplitude))+geom_line(size=1.5,color="#F9B90A7F",alpha=0.7)+
  xlab("Frequency (Hz)")+ylab("Spectral Amplitude")+
  theme_classic()+scale_x_continuous(breaks=seq(0,12,2))+ 
  theme(axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=16))
plot_100L
```

100% cue condition in **right visual field**
```{r echo=FALSE}
con100_R<-con100 %>% filter(Conditions=='R_100')
plot_100R<-ggplot(con100_R,aes(x=Hz,y=Amplitude))+geom_line(size=1.5,color="#F9B90A7F",alpha=0.7)+
  xlab("Frequency (Hz)")+ylab("Spectral Amplitude")+
  scale_x_continuous(breaks=seq(0,12,2))+theme_classic()+
  theme(axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=16))
plot_100R
```

grid plot of four images
```{r echo=FALSE}
plot_grid(plot_L50,plot_R50,plot_100L,plot_100R,nrow=2)
```


* find out **the peak frequencies**, they can be significant or not
```{r}
listcon<-list("L_val_50","L_inval_50","R_val_50","R_inval_50","L_100","R_100")
eachcon<-listcon %>% map(function(x) filter(long_all_con,Conditions==x))
names(eachcon)<-c("L_val_50","L_inval_50","R_val_50","R_inval_50","L_100","R_100")

eachcon %>% map(function(x) filter(x,Amplitude==max(x$Amplitude)))
```

* find out the second peak (can be significant or not)

```{r}
# print out the top 5 frequencies, which might include the second peak
eachcon %>% map(function(x) x %>% top_n(10,Amplitude))
```

