---
title: "Raw vs Smooth"
output: html_notebook
date: 12/30/2017
---

* This script will show how low pass Filters (cutoff: `8Hz`, order = 3) changes the results. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(cowplot)
```

### get valid subjects
```{r}
rm(list=ls())
outlier <- c(5,11,17,18) # the only variable needs to be changed
allsub <- c(1:19,24:36,38,40,41,43:46)
valid_sub <- setdiff(allsub,outlier) # get only valid subjects

subNo <- paste0("Sub",valid_sub)
```

### Left visual field

* con_50_left_valid  
```{r echo=FALSE}
val_or_not<-1
prefix<-"Con50L_valid_"
smoothpre<-'LP_Smoothed_Con50L_valid_'

Con50L_val.files<-vector()
Con50L_val.files.smooth<-vector()
for (i in seq_along(subNo)){
  Con50L_val.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con50L_val.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con50L_valid<-data_frame(filename=Con50L_val.files) %>% 
  mutate(raw=map(Con50L_val.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con50L_val.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_50_left_valid<- unnest(Con50L_valid) %>% rename(smooth=V2)
all_50_left_valid<- all_50_left_valid %>% mutate(val=rep(val_or_not,(dim(all_50_left_valid)[1]))) 
all_50_left_valid$val<-factor(all_50_left_valid$val)
```

* con_50_left_invalid  
```{r echo=FALSE}
val_or_not<-0
prefix<-"Con50L_invalid_"
smoothpre<-"LP_Smoothed_Con50L_invalid_"

Con50L_inval.files<-vector()
Con50L_inval.files.smooth<-vector()
for (i in seq_along(subNo)){
  Con50L_inval.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con50L_inval.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con50L_invalid<-data_frame(filename=Con50L_inval.files) %>% 
  mutate(raw=map(Con50L_inval.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con50L_inval.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_50_left_invalid<- unnest(Con50L_invalid) %>% rename(smooth=V2)
all_50_left_invalid<- all_50_left_invalid %>% mutate(val=rep(val_or_not,(dim(all_50_left_invalid)[1])))
all_50_left_invalid$val<-factor(all_50_left_invalid$val)
```

* combine con_50_left/valid-invalid  
```{r echo=FALSE}
all_50_left<-tbl_df(rbind(all_50_left_valid,all_50_left_invalid)) %>% select(-filename)
mean_all_50_left<- all_50_left %>% group_by(time,val) %>% summarise(Msmooth=mean(smooth),Merror=mean(error)) %>%
  gather(con,value,Msmooth:Merror) %>% unite(allcon,val,con,sep=".")
mean_all_50_left$allcon<-factor(mean_all_50_left$allcon)
```

* plot raw vs smooth (50 left)
```{r}
# old color system
#scale_color_manual(values=c("#4DBBD5B2","#4DBBD5B2","#E64B35B2","#E64B35B2"))

con50_L<-ggplot(mean_all_50_left,aes(x=time,y=value,alpha=allcon,color=allcon,size=allcon))+geom_line()+
  xlab('Cue-to-Probe Interval (s)')+
  ylab("Absolute Deviation (degrees)") + scale_alpha_manual(values = c(0.4,0.7,0.4,0.7))+
  scale_color_manual(values=c("#3D79F37F","#3D79F37F","#E6352F7F","#E6352F7F"))+  
  scale_size_manual(values=c(1,1.8,1,1.8))+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(size=20),
        axis.text.y=element_text(size=20),
        legend.position = "Null")+
  scale_x_continuous(breaks = seq(0.3,1.5,0.2))+
  scale_y_continuous(breaks = seq(12,20,2))+expand_limits(y = c(12,20))
##        blue         red      yellow       green 
## "#3D79F37F" "#E6352F7F" "#F9B90A7F" "#34A74B7F"


#   scale_color_discrete(name="Conditions",breaks=c("0.Merror","0.Msmooth","1.Merror","1.Msmooth"),
#                                          labels=c("Raw-Invalid","Smooth-Invalid","Raw-Valid","Smooth-Valid"))

con50_L
```

### right visual field

* con_50_right_valid
```{r echo=FALSE}
val_or_not<-1
prefix<-"Con50R_valid_"
smoothpre<-'LP_Smoothed_Con50R_valid_'

Con50R_val.files<-vector()
Con50R_val.files.smooth<-vector()
for (i in seq_along(subNo)){
  Con50R_val.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con50R_val.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con50R_valid<-data_frame(filename=Con50R_val.files) %>%
  mutate(raw=map(Con50R_val.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con50R_val.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_50_right_valid<-unnest(Con50R_valid) %>% rename(smooth=V2)
all_50_right_valid<-all_50_right_valid %>% mutate(val=rep(val_or_not,(dim(all_50_right_valid)[1]))) 
all_50_right_valid$val<-factor(all_50_right_valid$val)

```

* con_50_right_invalid
```{r echo=FALSE}
val_or_not<-0
prefix<-"Con50R_invalid_"
smoothpre<-'LP_Smoothed_Con50R_invalid_'


Con50R_inval.files<-vector()
Con50R_inval.files.smooth<-vector()
for (i in seq_along(subNo)){
  Con50R_inval.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con50R_inval.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con50R_invalid<-data_frame(filename=Con50R_inval.files) %>% 
  mutate(raw=map(Con50R_inval.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con50R_inval.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_50_right_invalid<- unnest(Con50R_invalid) %>% rename(smooth=V2)
all_50_right_invalid<- all_50_right_invalid %>% mutate(val=rep(val_or_not,(dim(all_50_right_invalid)[1]))) 
all_50_right_invalid$val<-factor(all_50_right_invalid$val)
```

* combine con_50_right/valid-invalid 
```{r echo=FALSE}
all_50_right<-tbl_df(rbind(all_50_right_valid,all_50_right_invalid)) %>% select(-filename)
mean_all_50_right<- all_50_right %>% group_by(time,val) %>% summarise(Msmooth=mean(smooth),Merror=mean(error)) %>%
  gather(con,value,Msmooth:Merror) %>% unite(allcon,val,con,sep=".")
mean_all_50_right$allcon<-factor(mean_all_50_right$allcon)
```

* plot raw vs smooth (50 right)

```{r}
con50_R<-ggplot(mean_all_50_right,aes(x=time,y=value,alpha=allcon,color=allcon,size=allcon))+
  geom_line()+ xlab("Cue-to-Probe Interval (s)")+
  labs(y="Absolute Deviation (degrees)") + scale_alpha_manual(values = c(0.4,0.7,0.4,0.7))+
  scale_color_manual(values=c("#3D79F37F","#3D79F37F","#E6352F7F","#E6352F7F"))+
  scale_size_manual(values=c(1,1.8,1,1.8))+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(size=20),
        axis.text.y=element_text(size=20),
        legend.position = "Null")+scale_x_continuous(breaks = seq(0.3,1.5,0.2))+
  scale_y_continuous(breaks = seq(12,20,2))+expand_limits(y = c(12,20))

con50_R
```

* **optional** save plots
```{r eval=FALSE, echo=FALSE}
# save figures
save_plot("LVF_50_smoothVSraw_74.pdf",con50_L)
save_plot("RVF_50_smoothVSraw_74.pdf",con50_R)
```


### 100 valid

* con_100_left
```{r echo=FALSE}
prefix<-"Con100L_"
smoothpre<-"LP_Smoothed_Con100L_"

Con100L.files<-vector()
Con100L.files.smooth<-vector()

for (i in seq_along(subNo)){
  Con100L.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con100L.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con100L<-data_frame(filename=Con100L.files) %>% 
  mutate(raw=map(Con100L.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con100L.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_100_left<- unnest(Con100L) %>% rename(smooth=V2)
mean_all_100_left<-all_100_left %>% select(-filename) %>% group_by(time) %>% summarise(Msmooth=mean(smooth),Merror=mean(error)) %>%
  gather(con,value,Msmooth:Merror)
mean_all_100_left$con<-factor(mean_all_100_left$con)
```

* plot raw vs smooth (100 left)
```{r}
# old color:geom_line(size=1,color="#3C5488B2") grey
# new color: "#F9B90A7F" google yellow
con100_L<-ggplot(mean_all_100_left,aes(x=time,y=value,alpha=con,size=con))+geom_line(color="#F9B90A7F")+
labs(y="Absolute Deviation (degrees)")+scale_alpha_manual(values=c(0.4,0.7))+
  scale_size_manual(values=c(1,1.8))+
  xlab("Cue-to-Probe Interval (s)")+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(size=20),
        axis.text.y=element_text(size=20),
        legend.position = "Null")+scale_x_continuous(breaks = seq(0.3,1.5,0.2))+
  scale_y_continuous(breaks = seq(11,17,2)) + expand_limits(y = c(11,17))
con100_L
```


* con_100_right
```{r echo=FALSE}
prefix<-"Con100R_"
smoothpre<-"LP_Smoothed_Con100R_"

Con100R.files<-vector()
Con100R.files.smooth<-vector()

for (i in seq_along(subNo)){
  Con100R.files[i]<-paste(prefix,subNo[i],".txt",sep="")
  Con100R.files.smooth[i]<-paste(smoothpre,subNo[i],".txt",sep="")
}
Con100R<-data_frame(filename=Con100R.files) %>% 
  mutate(raw=map(Con100R.files,function(x) read.table(x,colClasses =c("numeric","numeric"),col.names = c("time","error"))),
         smooth=map(Con100R.files.smooth,function(x) read.table(x,colClasses = c("NULL","numeric"))))

all_100_right<- unnest(Con100R) %>% rename(smooth=V2)
mean_all_100_right<-all_100_right %>% select(-filename) %>% group_by(time) %>% summarise(Msmooth=mean(smooth),Merror=mean(error)) %>%
  gather(con,value,Msmooth:Merror)
mean_all_100_right$con<-factor(mean_all_100_right$con)
```

* plot raw vs smooth (100 right)
```{r}
con100_R<-ggplot(mean_all_100_right,aes(x=time,y=value,alpha=con,size=con))+geom_line(color="#F9B90A7F")+
  scale_alpha_manual(values=c(0.4,0.7))+
  scale_size_manual(values=c(1,1.8))+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(size=20),
        axis.text.y=element_text(size=20),
        legend.position="Null")+scale_x_continuous(breaks = seq(0.3,1.5,0.2))+
  coord_cartesian(ylim = c(11,17)) + scale_y_continuous(breaks = seq(11,17,2))
con100_R
```

* **optional** save plots

```{r eval=FALSE,echo=FALSE}
# combine two plots     
Con100LR<-plot_grid(con100_L,con100_R,labels=c("A","B"),nrow=2,align="v")
save_plot("Meansub_Con100LR_smoothed.pdf",Con100LR,nrow=2,base_aspect_ratio = 1.3)
-----------------------------------------------------------------------------------
save_plot("LVF_100_smoothVSraw_74.pdf",con100_L)
save_plot("RVF_100_smoothVSraw_74.pdf",con100_R)
```

* **optional** combine all four plots
```{r}
# combine four plots: align plots with the same y axis (https://notesbytim.wordpress.com/2014/07/16/dual-ggplot2-different-chart-same-y-axis/)
# con50L.common.y <- ggplot_gtable(ggplot_build(con50_L))
# con50R.common.y <- ggplot_gtable(ggplot_build(con50_R))
# con50L.common.y$heights <- con50R.common.y$heights
# con50_all.common.y <- plot_grid(con50L.common.y,con50R.common.y,nrow = 1) 
# 
# con100L.common.y <- ggplot_gtable(ggplot_build(con100_L))
# con100R.common.y <- ggplot_gtable(ggplot_build(con100_R))
# con100L.common.y$heights <- con100R.common.y$heights
# con100_all.common.y <- plot_grid(con100L.common.y,con100R.common.y,nrow = 1) 
con_all<-plot_grid(con50_L,con50_R,con100_L,con100_R,nrow=2,align="h")
#con_all<-plot_grid(con50_all.common.y,con100_all.common.y,nrow=2,align="v")
con_all
```




